Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-12 doc/paper.tex
Some improvements in the paper

 We used two different kind of benchmark sets from~\cite{tomas2006visibility}:
     \begin{itemize}
     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas. They are specific because they have tiny interior. They presents a boundary case for the caardinality of set $D(P)$ which means that a very few points will be added in $D(P)$.
     	 \item \emph{FAT} instances:  includes polygons of large areas. They are specific because their interior is wide. In this case, a large number of points of relgular grid will be included into $D(P)$.
     \end{itemize}
     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons.
	We included two kind of weights into each of (194) instances:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,. a higher price.
		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|V(i)|}{|D(P)|},\ i=1,...,n.
		\end{equation}
    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher quality and thus of a higher price.
	\end{itemize}

@@

    \begin{figure}
    	\centering\scalebox{0.9}{
    	\includegraphics[width=\textwidth]{grafikon1.eps}}
    	\caption{Polygon coverage for the type of weight W0.}
    	\label{fig:covw0}
    \end{figure}

    \begin{figure}
    	\centering
    	\centering\scalebox{0.9}{
    	\includegraphics[width=\textwidth]{grafikon2.eps}}
    	\caption{Polygon coverage for the type of weight W1.}
    	\label{fig:covw1}
    \end{figure}

    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{grafikon3.eps}
    	\caption{Avg. execution time of the compared algorithms.}
    	\label{fig:timealg}
    \end{figure}

>>>>

 We used two different kind of benchmark sets from~\cite{tomas2006visibility}:
     \begin{itemize}
     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas. They are specific because they have tiny interior. They presents a boundary case for the caardinality of set $D(P)$ which means that a very few points will be added in $D(P)$.
     	 \item \emph{FAT} instances:  includes polygons of large areas. They are specific because their interior is wide. In this case, a large number of points of relgular grid will be included into $D(P)$.
     \end{itemize}
     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons.
	We included two kind of weights into each of (194) instances:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,. a higher price.
		\item \emph{point-based related weights} ($W1$): For each vertex $v_j$, based on the number of points in $D(P)$ that are visible from $v_j$, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|S_i|}{|D(P)|},\ i=1,...,n.
		\end{equation}
    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher spectrum and quality, and thus are more expensive. 
	\end{itemize}

@@

    \begin{figure}[!ht]
    	\centering\scalebox{0.9}{
    	\includegraphics[width=\textwidth]{grafikon1.eps}}
    	\caption{Polygon coverage for the type of weight W0.}
    	\label{fig:covw0}
    \end{figure}

    \begin{figure}[!ht]
    	\centering
    	\centering\scalebox{0.9}{
    	\includegraphics[width=\textwidth]{grafikon2.eps}}
    	\caption{Polygon coverage for the type of weight W1.}
    	\label{fig:covw1}
    \end{figure}

    \begin{figure}[!ht]
    	\centering
    	\includegraphics[width=\textwidth]{grafikon3.eps}
    	\caption{Avg. execution time of the compared algorithms.}
    	\label{fig:timealg}
    \end{figure}
